Crowdsourced geometric morphometrics enable rapid large-scale collection and

### 2015-04-22 manuscript/manuscript.Rmd
Try to cache most chunks, and don't echo anything

```{r prelude, echo=FALSE, message=FALSE, warning=FALSE}
library("MASS")
library("readr")
library("dplyr")
library("ggplot2")
library("stringr")
library("magrittr")
library("tidyr")
library("reshape2")
library("scales")
library("grid")
library("geomorph")
library("rjson")
library("ipred")
library("vegan")
library("lubridate")
library("directlabels")
library("BAMMtools")
library("knitcitations")
library("kfigr")
library("fish.reliability")
options("citation_format"="pandoc")
cleanbib()
set.seed(111) # reproducible and stable sampling
data(fish_landmarks)
data(fish_families)
```

@@

```{r geomorph_lm, eval=FALSE, cache=TRUE}
fmted <- format_for_gpagen(no_st)
allsplit <- str_split_fixed(dimnames(fmted)$id, "_", 3)
family_vec <- allsplit[, 1]
role_vec <- allsplit[, 2]
ind_vec <- allsplit[, 3]
gpaed <- gpagen(fmted, ShowPlot=F)

@@

```{r median_tbl, echo=F, results="asis", anchor="table", fig.cap="Median table"}
med_wide <- meds %>% spread(key=family, value=value)
med_wide %>% knitr::kable(digits = 2, caption = "Median table")
```

```{r mad_tbl, echo=F, results="asis", anchor="table", fig.cap="MAD table"}
mad_wide <- mads %>% spread(key=family, value=value)
mad_wide %>% knitr::kable(digits = 2, caption="MAD table")
```

@@

```{r cv_table, echo=F, results="asis", anchor="table", message=FALSE}

@@

```{r turk_morph_procrustes_space, echo=FALSE, fig.cap="Hello", fig.keep="last", anchor="figure", message=FALSE}

# Load data from the anonymized results file, remove students, drop bad marks
df <- fish_landmarks %>%
	filter(role != "student") %>% 
	separate(col=mark, into=c("cat", "cat_seq"), sep=1, remove=F, convert=T) %>%
	filter(!(family %in% c("Bal") & mark %in% c("D1","D2")), !mark %in% c("O1","O2","O3","O4","O5", "A3", "D3", "D4"))

@@

coords <- gpagen(format_for_gpagen(df), ShowPlot=F)$coords
```

Text text

```{r turk_morph_procrustes_space, echo=FALSE, fig.cap="Testing my figure", anchor="figure"}
plot_tangent_space(coords, "PC1", "PC2")
```

@@

```{r, echo=FALSE}
# use broken stick method to get the principal components stopping point

@@

```{r bamm_plots, echo=F, message=F, warning=F, anchor="figure", cache=T}
df <- fish_families %>% group_by(tip, mark, family) %>% summarise(x=median(x), y=median(y))

@@

```{r timing_plot, echo=FALSE, fig.cap="Line plot showing time to receive results for any given image (x axis) and the total fraction of the data set received (y axis). Landmarks were first received 6 minutes after creation of the Amazon MTurk task, and at least one replicate was received for every image at the 80 minute mark."}
# median time (in minutes) it takes an expert to measure these fishes
timings <- (no_st %>% group_by(role) %>% summarise(duration=median(duration))) %>% mutate(total_time=duration * nrow(res2))

@@

```{r turker_morph_procrustes_other_pc23, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="PC2 and PC3 for turker / morphologist Procrustes space"}
plot_tangent_space(coords, "PC2", "PC3")
```

```{r turker_morph_procrustes_other_pc34, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="PC3 and PC4 for turker / morphologist Procrustes space"}
plot_tangent_space(coords, "PC3", "PC4")
```

```{r turker_morph_procrustes_other_pc45, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="PC4 and PC5 for turker / morphologist Procrustes space"}
plot_tangent_space(coords, "PC4", "PC5")
```

@@

```{r knitcitations_write, echo=FALSE, message=FALSE}
write.bibtex(file="knitcitations.bib")
# Also download Mendeley bibliography
mendbib <- RCurl::getURL("https://www.dropbox.com/s/ehwm3c945k7rh0n/library.bib?dl=1", .opts=RCurl::curlOptions(followlocation=TRUE))
cat(mendbib, file="library.bib")
```

>>>>

```{r prelude, echo=FALSE, message=FALSE, warning=FALSE}
library("MASS")
library("readr")
library("dplyr")
library("ggplot2")
library("stringr")
library("magrittr")
library("tidyr")
library("reshape2")
library("scales")
library("grid")
library("geomorph")
library("rjson")
library("ipred")
library("vegan")
library("lubridate")
library("directlabels")
library("BAMMtools")
library("knitcitations")
library("kfigr")
library("fish.reliability")
options("citation_format"="pandoc")
cleanbib()
set.seed(111) # reproducible and stable sampling
data(fish_landmarks)
data(fish_families)
knitr::opts_chunk$set(echo=FALSE, cache=1)
```

@@

```{r geomorph_lm, eval=FALSE}
fmted <- format_for_gpagen(no_st)
allsplit <- str_split_fixed(dimnames(fmted)$id, "_", 3)
family_vec <- allsplit[, 1]
role_vec <- allsplit[, 2]
ind_vec <- allsplit[, 3]
gpaed <- gpagen(fmted, ShowPlot=F)

@@

```{r median_tbl, results="asis", anchor="table", fig.cap="Median table"}
med_wide <- meds %>% spread(key=family, value=value)
med_wide %>% knitr::kable(digits = 2, caption = "Median table")
```

```{r mad_tbl, results="asis", anchor="table", fig.cap="MAD table"}
mad_wide <- mads %>% spread(key=family, value=value)
mad_wide %>% knitr::kable(digits = 2, caption="MAD table")
```

@@

```{r cv_table, results="asis", anchor="table", message=FALSE}

@@

```{r turk_morph_procrustes_space, fig.cap="Hello", anchor="figure", message=FALSE}
# Load data from the anonymized results file, remove students, drop bad marks
df <- fish_landmarks %>%
	filter(role != "student") %>% 
	separate(col=mark, into=c("cat", "cat_seq"), sep=1, remove=F, convert=T) %>%
	filter(!(family %in% c("Bal") & mark %in% c("D1","D2")), !mark %in% c("O1","O2","O3","O4","O5", "A3", "D3", "D4"))

@@

coords <- gpagen(format_for_gpagen(df), ShowPlot=F)$coords

plot_tangent_space(coords, "PC1", "PC2")
```

@@

```{r brokenstick}
# use broken stick method to get the principal components stopping point

@@

```{r bamm_plots, message=F, warning=F, anchor="figure"}
df <- fish_families %>% group_by(tip, mark, family) %>% summarise(x=median(x), y=median(y))

@@

```{r timing_plot, fig.cap="Line plot showing time to receive results for any given image (x axis) and the total fraction of the data set received (y axis). Landmarks were first received 6 minutes after creation of the Amazon MTurk task, and at least one replicate was received for every image at the 80 minute mark."}
# median time (in minutes) it takes an expert to measure these fishes
timings <- (no_st %>% group_by(role) %>% summarise(duration=median(duration))) %>% mutate(total_time=duration * nrow(res2))

@@

```{r turker_morph_procrustes_other_pc23, message=FALSE, warning=FALSE, fig.cap="PC2 and PC3 for turker / morphologist Procrustes space"}
plot_tangent_space(coords, "PC2", "PC3")
```

```{r turker_morph_procrustes_other_pc34, message=FALSE, warning=FALSE, fig.cap="PC3 and PC4 for turker / morphologist Procrustes space"}
plot_tangent_space(coords, "PC3", "PC4")
```

```{r turker_morph_procrustes_other_pc45, message=FALSE, warning=FALSE, fig.cap="PC4 and PC5 for turker / morphologist Procrustes space"}
plot_tangent_space(coords, "PC4", "PC5")
```

@@

```{r knitcitations_write, message=FALSE}
write.bibtex(file="knitcitations.bib")
# Also download Mendeley bibliography
mendbib <- RCurl::getURL("https://www.dropbox.com/s/ehwm3c945k7rh0n/library.bib?dl=1", .opts=RCurl::curlOptions(followlocation=TRUE))
cat(mendbib, file="library.bib")
```
